Sequential rank agreement methods for comparison of ranked lists

### 2015-05-23 latex/paper.Rnw
Bug fixes

producelists <- function(x, y) {
    nitems <- length(y)
    index <- seq(1, nrow(golub))
                                        # d <- data.frame(y, x)

@@

                                        # Elastic net
    X <- scale(t(x))
    enet <- glmnet(X, y, family="binomial", alpha=.8)
    nyres <- cv.glmnet(X, y, family="binomial", alpha=.8)
    coefficients <- coef(enet, s=nyres$lambda.1se)[-1]
    nonzeros <- sum(coefficients!=0)
    list3 <- order(abs(coefficients), decreasing=TRUE)
    if (nonzeros==0) {
        list3[(nonzeros+1):nitems] <- 0
    } 
                                        # MIC
    MIC <- sapply(index, function(i) { mine(x[i,], y)$MIC})
    list4 <- order(MIC, decreasing=TRUE)

>>>>

producelists <- function(x, y) {
    nitems <- ncol(x)
    index <- seq(1, nrow(golub))
                                        # d <- data.frame(y, x)

@@

                                        # Elastic net
    X <- scale(t(x))
    enet <- glmnet(X, y, family="binomial", alpha=.8)
    nyres <- cv.glmnet(X, y, family="binomial", alpha=.8)
    coefficients <- coef(enet, s=nyres$lambda.1se)[-1]
    nonzeros <- sum(coefficients!=0)
    list3 <- order(abs(coefficients), decreasing=TRUE)
    if (nonzeros<nitems) {
        list3[(nonzeros+1):nitems] <- 0
    } 
                                        # MIC
    MIC <- sapply(index, function(i) { mine(x[i,], y)$MIC})
    list4 <- order(MIC, decreasing=TRUE)
